Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-07-05 results.tex
Added 'publish' target
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1253 ccdd05d5-56c1-461a-bf98-85f6876523b4
Merged two paragraphs in section 5.5
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1256 ccdd05d5-56c1-461a-bf98-85f6876523b4
657 chirp masses -> 657 points with chirp masses
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1264 ccdd05d5-56c1-461a-bf98-85f6876523b4

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \textsc{ns}--\textsc{ns}
masses.  We begin by constructing a template bank that spans component masses
from 1~to~3~$M_\odot$ using a simulated Advanced \LIGO{} noise
curve~\citep{ALIGONoise}.  This results in a grid of 98544 points, or
$2 \times 98544 = 197088$~templates.  Then we create sub-banks by partitioning
the parameter space by chirp mass.  We shall concentrate on a sub-bank with 657
chirp masses between 1.1955 and 1.2045~$M_\odot$, or $2 \times 657 = 1314$~templates.
Figure \ref{fig:tmpltbank} illustrates this procedure.
\begin{figure}[h]
	\plotone{figures/tmpltbank.pdf}
	\caption{\label{fig:tmpltbank}Source parameters selected for sub-bank used in this
case study, consisting of component masses $m_1$, $m_2$, between 1 and 3~$M_\odot$, and
chirp masses $\mathcal{M}$ between 1.1955 and 1.2045~$M_\odot$.}
\end{figure}
With this sub-bank we were able to construct an efficient time-slice decomposition
that consisted of 11 time slices with sample rates between 32 and 4096 Hz summarized
in Table~\ref{tab:time_slices}.
\begin{table*}
\caption{\label{tab:time_slices} Filter design sub-bank of 657 templates.  From left to right, this table shows the sample rate, time interval, number of samples, and number of orthogonal templates for each time slice.  We vary \SVD{} tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\begin{center}
\begin{minipage}[c]{0.4\textwidth}
\includegraphics{figures/envelope}
\end{minipage}
\begin{minipage}[c]{0.55\textwidth}
\begin{tabular}{rr@{,\,}lc*{6}{r}}
\tableline\tableline
\\ [-2ex]
$f^s$ & $[t^s$&$t^{s+1})$ & &\multicolumn{6}{c}{$-\log_{10}$ (1$-$\SVD{} tolerance)} \\% [1ex]
\cline{5-10}
\\[-2.5ex]
(Hz) & \multicolumn{2}{c}{(s)} & $N^s$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ \\ \tableline
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\tableline
\end{tabular}
\end{minipage}
\end{center}
\end{table*}
We use this sub-bank and decomposition for the remainder of this section.

@@

\begin{figure*}[b]
	\begin{minipage}[t]{0.5\textwidth}
		\begin{center}
			\includegraphics{figures/bw.pdf}
			(a) Mismatch versus \SVD\ tolerance
		\end{center}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\begin{center}
			\includegraphics{figures/bw_resample.pdf}
			(b) Mismatch versus $N^\shortuparrow$
		\end{center}
	\end{minipage}
	\caption{\label{fig:bw}Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse responses.  The upper and lower boundaries of
the boxes show the upper and lower quartiles; the lines in the center denote the medians.
The whiskers represent the minimum and maximum mismatch over all templates.  In 
(a) the interpolation filter length is held fixed at $N^\shortuparrow = 192$, while
the \SVD\ tolerance is varied from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.
In (b), the \SVD\ tolerance is fixed at $\left(1-10^{-6}\right)$ while $N^\shortuparrow$
is varied from 8 to 192 coefficients.}
\end{figure*}

@@

The 5~s latency is probably due to buffering and synchronization.  The latency
might be reduced by carefully tuning buffer lengths at every stage in
the pipeline.  The minimum theoretically possible latency is set by
$N^\shortdownarrow$ and $N^\shortuparrow$.

Even without further refinements, our implementation of the \lloid\ algorithm
achieves latencies that would make other aspects of the analysis the limiting
steps assuming that the human vetting process is automated.

>>>>

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \textsc{ns}--\textsc{ns}
masses.  We begin by constructing a template bank that spans component masses
from 1~to~3~$M_\odot$ using a simulated Advanced \LIGO{} noise
curve~\citep{ALIGONoise}.  This results in a grid of 98544 points, or
$2 \times 98544 = 197088$~templates.  Then we create sub-banks by partitioning
the parameter space by chirp mass.  We shall concentrate on a sub-bank with 657 points with
chirp masses between 1.1955 and 1.2045~$M_\odot$, or $2 \times 657 = 1314$~templates.
Figure \ref{fig:tmpltbank} illustrates this procedure.
\begin{figure}[h]
	\plotone{f4}
	\caption{\label{fig:tmpltbank}Source parameters selected for sub-bank used in this
case study, consisting of component masses $m_1$, $m_2$, between 1 and 3~$M_\odot$, and
chirp masses $\mathcal{M}$ between 1.1955 and 1.2045~$M_\odot$.}
\end{figure}
With this sub-bank we were able to construct an efficient time-slice decomposition
that consisted of 11 time slices with sample rates between 32 and 4096 Hz summarized
in Table~\ref{tab:time_slices}.
\begin{table*}
\caption{\label{tab:time_slices} Filter design sub-bank of 657 templates.  From left to right, this table shows the sample rate, time interval, number of samples, and number of orthogonal templates for each time slice.  We vary \SVD{} tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\begin{center}
\begin{minipage}[c]{0.4\textwidth}
\includegraphics{t3}
\end{minipage}
\begin{minipage}[c]{0.55\textwidth}
\begin{tabular}{rr@{,\,}lc*{6}{r}}
\tableline\tableline
\\ [-2ex]
$f^s$ & $[t^s$&$t^{s+1})$ & &\multicolumn{6}{c}{$-\log_{10}$ (1$-$\SVD{} tolerance)} \\% [1ex]
\cline{5-10}
\\[-2.5ex]
(Hz) & \multicolumn{2}{c}{(s)} & $N^s$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ \\ \tableline
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\tableline
\end{tabular}
\end{minipage}
\end{center}
\end{table*}
We use this sub-bank and decomposition for the remainder of this section.

@@

\begin{figure*}[b]
	\begin{minipage}[t]{0.5\textwidth}
		\begin{center}
			\includegraphics{f5a}
			(a) Mismatch versus \SVD\ tolerance
		\end{center}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\begin{center}
			\includegraphics{f5b}
			(b) Mismatch versus $N^\shortuparrow$
		\end{center}
	\end{minipage}
	\caption{\label{fig:bw}Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse responses.  The upper and lower boundaries of
the boxes show the upper and lower quartiles; the lines in the center denote the medians.
The whiskers represent the minimum and maximum mismatch over all templates.  In 
(a) the interpolation filter length is held fixed at $N^\shortuparrow = 192$, while
the \SVD\ tolerance is varied from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.
In (b), the \SVD\ tolerance is fixed at $\left(1-10^{-6}\right)$ while $N^\shortuparrow$
is varied from 8 to 192 coefficients.}
\end{figure*}

@@

The 5~s latency is probably due to buffering and synchronization.  The latency
might be reduced by carefully tuning buffer lengths at every stage in
the pipeline.  The minimum theoretically possible latency is set by
$N^\shortdownarrow$ and $N^\shortuparrow$.
Even without further refinements, our implementation of the \lloid\ algorithm
achieves latencies that would make other aspects of the analysis the limiting
steps assuming that the human vetting process is automated.
